---
title: "EnawoMap"
author: "Kelly Hondula"
date: "5/5/2017"
output:
  html_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

Load up some libraries

```{r}
library(leaflet)
library(sp)
library(rgdal)
```

# Data sources

## UNOSAT data

Inundation shapefiles developed by UNOSAT downloaded from [here](http://www.unitar.org/unosat/maps/MDG).

* `flooding03010`: flooding extent on March 10th
* `extent0310`: bounding box of flooding extent analyzed on March 10th
* `flooding0308`: flooding extent on March 8th
* `extent0308`: bounding box of flooding extent analyzed on March 8th
* `floodbase_2014`: normal amount of flooding


```{r}
flooding0310 <- readOGR("TC20170306MDG_SHP",
                  "TSX_20170310_SatelliteDetectedSurfaceWaters_Maroantsetra")
extent0310 <- readOGR("TC20170306MDG_SHP",
                      "TSX_20170310_Analysis_Extent")
flooding0308 <- readOGR("TC20170306MDG_SHP",
                        "TSX_20170308_SatelliteDetectedSurfaceWaters_Maroantsetra")
extent0308 <- readOGR("TC20170306MDG_SHP",
                      "TSX_20170308_RS2_20140504_Analysis_Extent")
floodbase_2014 <- readOGR("TC20170306MDG_SHP",
                          "RS2_20140504_SatelliteDetectedSurfaceWaters_Maroantsetra")
```

## Village locations

Read in data with coordinates of villages

```{r}
darwinpts <- read.csv(file = "darwin2.csv", stringsAsFactors = FALSE)

darwinpts$lat <- sapply(darwinpts$S, function(x) {
  -1*(as.numeric(unlist(strsplit(x, " "))[1])+
        as.numeric(unlist(strsplit(x, " "))[2])/60 +
        as.numeric(unlist(strsplit(x, " "))[3])/3600)
})  

darwinpts$lon <- sapply(darwinpts$E, function(x) {
  as.numeric(unlist(strsplit(x, " "))[1])+
    as.numeric(unlist(strsplit(x, " "))[2])/60 +
    as.numeric(unlist(strsplit(x, " "))[3])/3600
})
```

## Hurricane Track

```{r}
# Hurricane track data: http://weather.unisys.com/hurricane/s_indian/2017/ENAWO/track.dat
# Using method from `https://rud.is/b/2015/08/20/track-hurricane-danny-with-r-leaflet/`

library(stringi)
enawo_track <- 
  readLines("http://weather.unisys.com/hurricane/s_indian/2017/ENAWO/track.dat")

enawo_track <- read.table(textConnection(gsub("TROPICAL ", "TROPICAL_", enawo_track[3:length(enawo_track)])), 
                          header=TRUE, stringsAsFactors=FALSE)

# make storm type names prettier
enawo_track$STAT <- stri_trans_totitle(gsub("_", " ", enawo_track$STAT))

# make column names prettier
colnames(enawo_track) <- c("advisory", "lat", "lon", "time", "wind_speed", "pressure", "status")

```

# Maps

```{r}
leaflet() %>% 
  addTiles(group = "OSM (default)") %>%
  addProviderTiles("Esri.WorldImagery", group = "Esri base") %>%
  addMarkers(data=darwinpts, ~lon, ~lat, group = "villages as markers", popup = ~Village) %>%
  addPolylines(data=enawo_track, ~lon, ~lat, color = "yellow", group = "path") %>%
  addPolygons(data = flooding0310, col = "red", group = "Flood Mar 10" ) %>%
  addPolygons(data = flooding0308, col = "purple", group = "Flood Mar 08") %>%
  addPolygons(data = extent0310, col = "black", fillOpacity = 0) %>%
  addPolygons(data = extent0308, col = "black", fillOpacity = 0) %>%
  addPolygons(data = floodbase_2014, col = "blue", group = "Flood 2014") %>%  addTiles(paste0('http://map1{s}.vis.earthdata.nasa.gov/wmts-webmerc/',
                  "VIIRS_SNPP_CorrectedReflectance_TrueColor",
                  '/default/',
                  "2017-03-07",'/',
                  "GoogleMapsCompatible_Level9",'/{z}/{y}/{x}.',"jpeg"),
           attribution = paste(
             '<a href="https://earthdata.nasa.gov/gibs">NASA EOSDIS GIBS</a>'
           ),
           options = list(
             # maxZoom = zoomLvl,
             minZoom = 1,
             tileSize = 256,
             subdomains = "abc",
             noWrap = "true",
             crs = "L.CRS.EPSG3857",    
             continuousWorld = "true",
             # Prevent Leaflet from retrieving non-existent tiles on the borders.
             bounds = list(list(-85.0511287776, -179.999999975),
                           list(85.0511287776, 179.999999975))
           ), group = "VIIRS") %>%
  addTiles(paste0('http://map1.vis.earthdata.nasa.gov/wmts-webmerc/',
                  "AMSR2_Surface_Precipitation_Rate_Day",
                  '/default/',
                  "2017-03-07",'/',
                  "GoogleMapsCompatible_Level6",
                  '/{z}/{y}/{x}.'
                  ,"png"),
           options = list(
             # maxZoom = 9,
             # maxNativeZoom = olzoomLvl[i],
             minZoom = 1,
             tileSize = 256,
             subdomains = "abc",
             noWrap = "true",
             crs = "L.CRS.EPSG3857",    
             continuousWorld = "true",
             opacity = 0.6,
             # Prevent Leaflet from retrieving non-existent tiles on the borders.
             bounds = list(list(-85.0511287776, -179.999999975),
                           list(85.0511287776, 179.999999975))
           ), group = "Surface Precip") %>%
  addTiles(paste0('http://map1.vis.earthdata.nasa.gov/wmts-webmerc/',
                  "AMSR2_Surface_Precipitation_Rate_Night",
                  '/default/',
                  "2017-03-07",'/',
                  "GoogleMapsCompatible_Level6",
                  '/{z}/{y}/{x}.'
                  ,"png"),
           options = list(
             # maxZoom = 9,
             # maxNativeZoom = olzoomLvl[i],
             minZoom = 1,
             tileSize = 256,
             subdomains = "abc",
             noWrap = "true",
             crs = "L.CRS.EPSG3857",    
             continuousWorld = "true",
             opacity = 0.6,
             # Prevent Leaflet from retrieving non-existent tiles on the borders.
             bounds = list(list(-85.0511287776, -179.999999975),
                           list(85.0511287776, 179.999999975))
           ), group = "Surface Precip") %>%
  addTiles(paste0('https://gibs.earthdata.nasa.gov/wmts/epsg3857/best/Coastlines/default/',
                  "GoogleMapsCompatible_Level9",
                  '/{z}/{y}/{x}.'
                  ,"png"),
           options = list(
             # maxZoom = 9,
             # maxNativeZoom = olzoomLvl[i],
             minZoom = 1,
             tileSize = 256,
             subdomains = "abc",
             noWrap = "true",
             crs = "L.CRS.EPSG3857",    
             continuousWorld = "true",
             opacity = 0.6,
             # Prevent Leaflet from retrieving non-existent tiles on the borders.
             bounds = list(list(-85.0511287776, -179.999999975),
                           list(85.0511287776, 179.999999975))
           ), group = "coast") %>%
  addLayersControl(
    baseGroups = c("OSM (default)", "Esri base", "VIIRS"),
    overlayGroups = c("coast", "Surface Precip", "villages as markers", "villages as circles", "path"),
    options = layersControlOptions(collapsed = TRUE))
```

